### 2018-08-06 paper/security-discussion.tex

@@

\sonja{Failure, exception handling, such as reordered chunks, chunks
  on different devices, squad devices going offline during transfer}
\commentDaniel{Reordered chunks is not a problem, we handle that.}

\section{Alternatives}%
\label{Alternatives}

\subsection{Stateful \name}
\subsection{Beyond file exchange} web browsing, hidden services,
interaction and collaboration.
\subsection{Other predictions} time of day?

>>>>

We base our solution on Sphinx, which, when used for onion routing, has been proved to satisfy the
properties given in ~cite{CLOnionRouting} that were shown to result
in a UC-secure onion-routing scheme. We thus primarily need to ensure that 
\begin{enumerate*} \item our extension to Sphinxes preserves these
  properties, \item the availability information introduced and
  disseminated to deal with churn satisfies the device-unlinkability
  property we defined in~\cref{system-model}, and that \item the node
  selection does not introduce any advantage for the
  adversary. \end{enumerate*} In terms of general system robustness, a
stateless routing protocol needs to handle packet re-ordering and
network failures (links or nodes).

@@

\paragraph*{Robustness}

Stateless routing can result in re-ordered chunks or packets, and
chunks received on different devices of a user's squad. From
Sphinx, we inherit IDs for packets that we we include in the
out-of-band metadata on the file to be exchanged, as an ordered list,
that is used to re-order chunks if need be. The squad overlay handles
inter-squad device coordination. Liveness despite the possibility of squad devices going offline during
transfer or other node or link failures is ensured by acknowledgments
and timeouts as detailed in ~\cref{sec:squad_overlay}.

### 2018-08-06 paper/system-model.tex

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
onion-correctness, integrity, and security %(wrap resistance,
                                %indistinguishability). 
Informally, onion-correctness means that if an onion is formed
correctly, processed by the correct routers in the correct order, then
the correct message is received by the last router. Onion-integrity
means that even for an onion created by an adversary, the path length
is bounded by $N$. Onion-security means that an adversary sending a
challenge onion to a router and able to see the outcome of how the
onion is processed, cannot distinguish between whether that onion
corresponds to a particular message and route or not. This is also
true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
another layer. The formal definitions are in~cite{CLOnionRoutin} along
with a theorem that states that an onion routing scheme satisfying
these three properties, combined with secure point-to-point channels,
is UC-secure.

>>>>

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysyanskaya~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
onion-correctness, integrity, and security %(wrap resistance,
                                %indistinguishability). 
Informally, onion-correctness means that if an onion is formed
correctly, processed by the correct routers in the correct order, then
the correct message is received by the last router. Onion-integrity
means that even for an onion created by an adversary, the path length
is bounded by $N$. Onion-security means that an adversary sending a
challenge onion to a router and able to see the outcome of how the
onion is processed, cannot distinguish between whether that onion
corresponds to a particular message and route or not. This is also
true for a \emph{re-wrapped} onion, i.e. a challenge onion wrapped in
another layer. The formal definitions are in~\cite{CLOnionRouting} along
with a theorem that states that an onion routing scheme satisfying
these three properties, combined with secure point-to-point channels,
is UC-secure.
